---
title: "Assignment 5"
author: "Tucker Harris"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)   # loading ggplot2 and dplyr
library(patchwork)   # arranging multiple graphs into 1 figure
library(viridis)     # The viridis color schemes
library(latex2exp)   # For plotting math notation
library(plotly)     # for interactive hover-text
library(faraway)
library(ggrepel)
```


## Question 1 ab)

I know we never learned the force command, but for some reason this was the only way it would let me load the dataset.

I also made this graph before looking at parts a-b. I thought those were adjustments for after making the first graph.

```{r}
MortRate <- force(infmort)

Plot1 <- ggplot( MortRate, aes( x = log10( mortality ), y = log10(income), color = oil ) )+
  geom_point() +
  facet_grid(.~region)


Plot1
```

## Question 1c)

```{r}


Plot2 <- ggplot( MortRate, aes( x = mortality, y = income, color = oil ) )+
  geom_point() +
  facet_grid(.~region) +
  scale_x_log10() +
  scale_y_log10()




Plot2




```
I prefer to just use the log10 function inside the aes function.




##1d

I had this graph label all countries that are below S on an alphabetical list.

```{r}

MortRate2 <- MortRate %>% mutate(country = rownames(MortRate))

MortRate2 <- MortRate2 %>% mutate(partialCountry = str_remove_all(country, "^[A-S].*"))



Plot3 <- ggplot( MortRate2, aes( x = log10( mortality ), label = partialCountry, y = log10(income), color = oil ) )+
  geom_point() +
  facet_grid(.~region) +
  geom_label_repel()
  

Plot3
```



## Question 2a

```{r}

data(trees)



treeModel <- lm(trees$Volume~trees$Height)

treeModel
```

## Question 2b)
```{r}
summary(treeModel)
```

## Question 2c

```{r}
ggplot(treeModel, aes( x = trees$Height, y = trees$Volume ) ) +
  geom_point() 
```

## Question 2d

```{r}
ggplot(treeModel, aes( x = trees$Height, y = trees$Volume ) ) +
  geom_point() + 
  annotate('rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black') 
  
```

## Queston 2e

```{r}
ggplot( treeModel, aes( x = trees$Height, y = trees$Volume ) ) +
  geom_point() + 
  annotate( 'rect', xmin=65, xmax=75, ymin=60, ymax=74,
         fill='white', color='black' ) +
  annotate( 'text', x = 70, y = 67, size=5, color='purple', label='yhat = -87.12 + 1.54Xi' )
```

## Question 2f

```{r}
TwolabelTreePlot <- ggplot( treeModel, aes( x = trees$Height, y = trees$Volume ) ) +
  geom_point() + 
  annotate( 'rect', xmin=60, xmax=70, ymin=65, ymax=79,
         fill='white', color='black' ) +
  annotate( 'text', x = 65, y = 72, size=5, color='purple', label='yhat = -87.12 + 1.54Xi' ) +
  annotate( 'rect', xmin=60, xmax=70, ymin=45, ymax=59,
            fill='white', color='black' ) +
  annotate('text', x = 65, y = 52, size = 5, color ='purple', label='R^2 = 0.358')

TwolabelTreePlot
```

## Question 2g 

```{r}

TwolabelTreePlot + geom_abline(intercept = -87.12, slope = 1.54, color = 'red', size = 3)

```