---
title: "445_Assignment_4"
author: "Tucker Harris"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse)
```

## Question 1a
```{r}
Survey <- 
  read.csv('https://www.lock5stat.com/datasets3e/StudentSurvey.csv',
           na.strings=c('',' '))

head(Survey)

```

## Question 1b)
```{r}
SurveyA <- count( Survey, Year, Sex )

SurveyA <- SurveyA %>% drop_na()

SurveyA

# I could not figure out how to order the Years. I will hopefully have time to return to this later

```

## Question 1c)

```{r}
SurveyB <- SurveyA %>% pivot_wider(names_from = Year, values_from = n)


SurveyB 


```

## Question 2a)

```{r}

Temperature <-  read.csv('https://raw.githubusercontent.com/dereksonderegger/444/master/data-raw/FlagMaxTemp.csv', na.strings=c('NA',' '))

head(Temperature)

Temperature05 <- Temperature %>% filter (Year == 2005)

Temperature1 <- Temperature05 %>% pivot_longer(X1:X31, names_to = "Day", values_to = "Temperature")


Temperature1 <- Temperature1 %>% mutate(Day = str_remove_all( Day, 'X'))

DayTemp <- Temperature1 %>% mutate(date = make_date(year = Year, month = Month, day = Day))

DayTemp1 <- DayTemp %>% select( Temperature, date )

DayTemp1 <- DayTemp1 %>% mutate(Temperature = as.numeric(Temperature))

ggplot( data = DayTemp1, aes(x=date, y=Temperature) ) + geom_point() +
  labs("Daily 2005 temperatures", x = "Date", y = "Temperature" )

```
## Question 2b)

```{r}
Temperature1315 <- Temperature %>% filter(Year >= 2013 & Year <= 2015)

Temp1 <- Temperature1315 %>% pivot_longer(X1:X31, names_to = "Day", values_to = "Temperature")

Temp1<- Temp1 %>% drop_na()

Temp1 <- Temp1 %>% mutate(Day = str_remove_all( Day, 'X'))

Temp1 <- Temp1 %>% mutate(date = make_date(year = Year, month = Month))

Temp1 <- Temp1 %>% group_by(Year, Month) %>% summarize(meanTemp = mean(Temperature))


Temp1

ggplot( data = Temp1, aes(x = Month, y = meanTemp, color = Year)) + geom_point()


```

## Question 4 a

```{r}
A <- tribble(
  ~Name, ~Car,
  'Alice', 'Ford F150',
  'Bob',   'Tesla Model III',
  'Charlie', 'VW Bug')

B <- tribble(
  ~First.Name, ~Pet,
  'Bob',  'Cat',
  'Charlie', 'Dog',
  'Alice', 'Rabbit')

B <- B %>% arrange(First.Name)


AB <- cbind(A,B) %>% select(Name, Car, Pet)
AB

B <- B %>% rename("Name" = "First.Name")

full_join(A, B)
```

## Question 3b)

```{r}
C <- tibble( Name = 'Alice', Pet = 'Guinea Pig')
B <- rbind(B, C)

B




```
## Question 3c)


```{r}

full_join(A,B)

```
Using Join is so much easier, as I could not figure out how to use cbind in this case. The number of rows being different gave me an error, so I was only able to use a join.

## Question 4

```{r}
Customers <- tribble(
  ~PersonID, ~Name, ~Street, ~City, ~State,
  1, 'Derek Sonderegger',  '231 River Run', 'Flagstaff', 'AZ',
  2, 'Aubrey Sonderegger', '231 River Run', 'Flagstaff', 'AZ',
  3, 'Robert Buscaglia', '754 Forest Heights', 'Flagstaff', 'AZ',
  4, 'Roy St Laurent', '845 Elk View', 'Flagstaff', 'AZ')

Retailers <- tribble(
  ~RetailID, ~Name, ~Street, ~City, ~State,
  1, 'Kickstand Kafe', '719 N Humphreys St', 'Flagstaff', 'AZ',
  2, 'MartAnnes', '112 E Route 66', 'Flagstaff', 'AZ',
  3, 'REI', '323 S Windsor Ln', 'Flagstaff', 'AZ' )

Cards <- tribble(
  ~CardID, ~PersonID, ~Issue_DateTime, ~Exp_DateTime,
  '9876768717278723',  1,  '2019-9-20 0:00:00', '2022-9-20 0:00:00',
  '5628927579821287',  2,  '2019-9-20 0:00:00', '2022-9-20 0:00:00',
  '7295825498122734',  3,  '2019-9-28 0:00:00', '2022-9-28 0:00:00',
  '8723768965231926',  4,  '2019-9-30 0:00:00', '2022-9-30 0:00:00' ) 

Transactions <- tribble(
  ~CardID, ~RetailID, ~DateTime, ~Amount,
  '9876768717278723', 1, '2019-10-1 8:31:23',    5.68,
  '7295825498122734', 2, '2019-10-1 12:45:45',  25.67,
  '9876768717278723', 1, '2019-10-2 8:26:31',    5.68,
  '9876768717278723', 1, '2019-10-2 8:30:09',    9.23,
  '5628927579821287', 3, '2019-10-5 18:58:57',  68.54,
  '7295825498122734', 2, '2019-10-5 12:39:26',  31.84,
  '8723768965231926', 2, '2019-10-10 19:02:20', 42.83) 

Cards <- Cards %>% 
  mutate( Issue_DateTime = lubridate::ymd_hms(Issue_DateTime),
          Exp_DateTime   = lubridate::ymd_hms(Exp_DateTime) )
Transactions <- Transactions %>% 
  mutate( DateTime = lubridate::ymd_hms(DateTime))



```

## A

```{r}
# Filter Transactions for Derek
derek_transactions <- Customers %>% 
 filter(Name == 'Derek Sonderegger') 

derek_transactions <- derek_transactions %>%
 left_join(Cards, by = "PersonID") %>%
 left_join(Transactions, by = "CardID") 

derek_transactions <- derek_transactions %>%
 left_join(Retailers, by = "RetailID") %>%
 select(DateTime, Amount, Name = Name.x)

derek_transactions


```

## B
```{r}
# Find Aubrey's card details
aubrey_card_info <- Customers %>%
  filter(Name == 'Aubrey Sonderegger') %>%
  left_join(Cards, by = "PersonID")

aubrey_card_info

# Get CardID and PersonID for Aubrey
cardID <- aubrey_card_info$CardID

cardID

personID <- aubrey_card_info$PersonID

personID

# Close the existing card (set Exp_DateTime to the time it's closed)
close_time <- ymd_hms('2019-10-15 16:28:21')

close_time

Cards <- Cards %>%
  mutate(Exp_DateTime = ifelse(CardID == cardID, close_time, Exp_DateTime))

Cards

# Generate a new CardID for Aubrey's new card (you can make up a new number)
new_card_id <- '0321200302132003'

# Insert the new card into the Cards table
new_card <- tibble(CardID = new_card_id, PersonID = personID,
                    Issue_DateTime = close_time,
                    Exp_DateTime = close_time + years(3))  # Set a new expiration date

new_card

Cards <- rbind(Cards, new_card)

Cards


```
I added the new card in three times. I am not exactly sure how I did that or how to fix it.


## C
```{r}

# Define the transaction details
card <- new_card_id  # Use Aubrey's new card ID
retailid <- 1  # Retailer ID for Kickstand Kafe
datetime <- ymd_hms('2019-10-16 14:30:21')
amount <- 4.98

# Create a new transaction
new_transaction <- tibble(CardID = card, RetailID = retailid, DateTime = datetime, Amount = amount)

# Append the new transaction to the Transactions table
Transactions <- rbind(Transactions, new_transaction)



Transactions

```

## D
```{r}
# Define the transaction details
card <- '9876768717278723'  # OLD credit card
retailid <- 2  # Retailer ID for REI
datetime <- ymd_hms('2019-10-17 12:00:00')
amount <- 100.00  # Example amount

# Check if the card is currently valid
Valid_Cards <- Cards %>% 
  filter(CardID == card, Issue_DateTime <= datetime, datetime <= Exp_DateTime)

# If the card is valid, insert the transaction into the table
if (nrow(Valid_Cards) == 1) {
  new_transaction <- tibble(CardID = card, RetailID = retailid, DateTime = datetime, Amount = amount)
  Transactions <- rbind(Transactions, new_transaction)
} else {
  print('Card Denied')
}
```

This does not print anything :(. I am not sure where my code is wrong.


## E

```{r}

# Find Aubrey's card details
aubrey_card_info <- Customers %>%
  filter(Name == 'Aubrey Sonderegger') %>%
  left_join(Cards, by = "PersonID")

# Get Aubrey's CardIDs
aubrey_card_ids <- aubrey_card_info$CardID

# Filter and join transactions and retailer names for Aubrey's cards
aubrey_statement <- Transactions %>%
  filter(CardID %in% aubrey_card_ids) %>%
  left_join(Retailers, by = "RetailID") %>%
  select(DateTime, Amount, Name)

aubrey_statement


```

