---
title: "445_Assignment_1"
author: "Tucker Harris"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Chapter 8 Question 1


```{r}
vec_a<-c( 2, 4, 6 )
vec_b<-c( 8, 10, 12 )
vec_c<-vec_a + vec_b

vec_c
```

## Chapter 8 Question 2

``` {r}
vec_d <- c( 14, 20 )
vec_d + vec_a

# This adds va[1] + vd[1], va[2] + vd[2], va[3] + vd[1]

# The shorter vector merely repeats once it runs out of elements

# the warning is merely saying that one is shorter than the other

```

## Chapter 8 Question 3

``` {r}
vec_a + 5

# This merely added a 5 to each element within vec_a, there is no warning
# Because there is no vector end bound breached.
```


## Chapter 8 Question 4

```{r}

seq_vec <- seq(1,5,1)
colon_vec <- 1:5

seq_vec
colon_vec



```



## Chapter 8 Question 5

```{r}

even_seq <- seq(2, 20, 2)
even_col <- 2 * 1:10

even_seq
even_col


```


## Chapter 8 Question 6

```{r}

seq(0,1,length.out=21)

# Can also do this

seq(0,1,0.05) 
# But less efficient, as sometimes it may not be as nice of a number
# As 0.05, so using the length.out makes the computer figure out the math for you

```

## Chapter 8 Question 7

```{r}

rep( c( 2, 4, 8 ), 3 )

```

## Chapter 8 Question 8

```{r}

 rep( c( 2, 4, 8 ), each = 4)



```


## Chapter 8 Question 10

```{r}

M <- matrix( seq( 2, 30, 2 ), nrow = 3, byrow=TRUE )
M

a <- seq( 2, 10, 2 )
b <- seq( 12, 20, 2 )
c <- seq( 22, 30, 2 )


M <- rbind(a,b,c)

M

```


## Chapter 8 Question 12

```{r}
df <- data.frame(name= c('Alice','Bob','Charlie','Daniel'),
                 Grade = c(6,8,NA,9))

df[ -which(  is.na(df$Grade) ), ]
df[  which( !is.na(df$Grade) ), ]




```

The first method manually places values and column names into a new matrix. First way that NA is taken out of the matrix is by merely subtracting the df$Grade values with the na value. The second way uses the ! (not) operator. That says display all the values that are not "na"


## Chapter 8 Question 14

``` {r}

x = c(4,5,6,7,8,9,10)
y = c(34,35,41,40,45,47,51)
slope = 2.82
p.value = 0.000131

my.test <- list( x = x, y = y, Slope = slope, P = p.value )

my.test

my.test[2]

my.test['P']


```
## Chapter 9 Question 1

```{r}

library(tidyverse)
library(readxl)
library(googlesheets4)

```
Use file --> import dataset to bring the "Raw Data" page into R Studio. I also told it to skip rows 1:4, as those are either headers or empty.

```{r}
tree <- read_excel('Example_5.xls', range = "A5:C36", sheet = 2 ) 

str( tree )


```
The three columns and 31 rows are displayed appropriately.



## Chapter 9 Question 2

File -> Import Dataset, then select Example_3.xls

```{r}

tesla <- read_excel('Example_3.xls', range = "A1:L34", na = "-9999", sheet = 2 )


tail(tesla)

```

