---
title: "445_Assignment_3"
author: "Tucker Harris"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
library(tidyverse) 
library(stringr)   # tidyverse string functions, not loaded with tidyverse 
library(refinr)    # fuzzy string matching

library(lubridate)
```

## Chapter 11 question 1a

This detects when a string in the list of strings contains the character 'a'. This can be seen when plugging in three words with the letter a, and one without.

```{r}
strings <- c("Alphabet", "Airplane","Frog", "Zebra" )
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, 'a') )


```

b.)

This detect will determine if a given string contains the substring 'ab' in the word.This is case sensitive.

```{r}

strings <- c("Falling", "into", "The", "abyss")
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, 'ab') )




```
c.) This will search for the string containing an 'a' or a 'b', the brackets do not need to be a part of the string.

```{r}

strings <- c("[ab]", "climb", "cook", "beef", "alone")
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '[ab]') )




```
d.)

This expression determines if it starts with either an 'a' or a 'b'. This is still case sensitive, and the word can start with either or both characters. 


```{r}
strings <- c("aa", "B", "A", "bean", "Clip")
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '^[ab]') )

```
e.)

This should match any digit directly followed by white space with the next character being an 'a' or an 'A'

```{r}
strings <- c("1 a", "5 khaki", "16 alone", "18a", "Scoring A 95", "88 was the class average")
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '\\d+\\s[aA]') )


```
f.) This string matches a digit directly followed by either the character 'a' or 'A' whether or not there is white space in between the digit and the character. 

```{r}
strings <- c("6a", "6      ba", "4        ab", "778Alkaline")
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '\\d+\\s*[aA]') )


```
g.) This regular expression matches: a string with any character

```{r}
strings <- c("", "16", "This", 16)
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '.*') )


```

```{r} 
strings <- c("ffbar", "foo.bar", "%%bar", "foobar")
data.frame( string = strings ) %>%
  mutate( result = str_detect(string, '(foo\\.bar)|(^\\w{2}bar)') )

```
## Chapter 11 Question 2

```{r}

file.names <- c( 'S123.P2.C10_20120621_213422.jpg',
                 'S10.P1.C1_20120622_050148.jpg',
                 'S187.P2.C2_20120702_023501.jpg')

x1 <- str_replace_all(file.names, pattern = '_', replacement = '.')

x2 <- str_split_fixed( x1, pattern = '\\.', n = 6 )

year <- str_sub(x2[,4], start = 1, end = 4 )

month <- str_sub(x2[,4], start = 5, end = 6)

day <- str_sub(x2[,4], start = 7, end = 8)

hour <- str_sub(x2[,5], start = 1, end = 2)

minute <- str_sub(x2[,5], start = 3, end = 4)

second <- str_sub(x2[,5], start = 5, end = 6)

Site <- x2[,1]

Plot <- x2[,2]

Camera <- x2[,3]

data.frame(
  site = Site,
  plot = Plot,
  camera = Camera,
  year = year,
  month = month,
  day = day,
  hour = hour,
  minute = minute,
  second = second
  
  
)



```
## Chapter 11 Question 3

```{r}

Gettysburg <- 'Four score and seven years ago our fathers brought forth on this 
continent, a new nation, conceived in Liberty, and dedicated to the proposition 
that all men are created equal.

Now we are engaged in a great civil war, testing whether that nation, or any 
nation so conceived and so dedicated, can long endure. We are met on a great 
battle-field of that war. We have come to dedicate a portion of that field, as 
a final resting place for those who here gave their lives that that nation might 
live. It is altogether fitting and proper that we should do this.

But, in a larger sense, we can not dedicate -- we can not consecrate -- we can 
not hallow -- this ground. The brave men, living and dead, who struggled here, 
have consecrated it, far above our poor power to add or detract. The world will 
little note, nor long remember what we say here, but it can never forget what 
they did here. It is for us the living, rather, to be dedicated here to the 
unfinished work which they who fought here have thus far so nobly advanced. It 
is rather for us to be here dedicated to the great task remaining before us -- 
that from these honored dead we take increased devotion to that cause for which 
they gave the last full measure of devotion -- that we here highly resolve that 
these dead shall not have died in vain -- that this nation, under God, shall 
have a new birth of freedom -- and that government of the people, by the people, 
for the people, shall not perish from the earth.'


Gettysburg <- str_remove_all(Gettysburg, '\\.')

Gettysburg <- str_remove_all(Gettysburg, ',')

Gettysburg <- str_remove_all(Gettysburg, '-')

Gettysburg <- str_trim(Gettysburg)

splitBurg <- str_split(Gettysburg, '\\s+')

# splitBurg[[1]]

speechLength <- length(splitBurg[[1]])

speechChars <- sum(str_length(splitBurg[[1]]))

# The average word length is now the sum of the length divided by the number of words.

speechChars / speechLength

```

For some reason, I was unable to compile with part h and part i. I had those working, but they would not compile for some reason. I apologize for that.

## Chapter 12 question 1

```{r}
TimeObject1 <- 'September 13, 2010' 

mdy(TimeObject1)

TimeObject2 <- 'Sept 13, 2010'

as.Date(TimeObject2, format = '%b %d, %Y')
# This one comes out as NA, I believe it cannot read it in the format it was given. However, it is better than coming through as an error, which is what happens when trying the mdy function

mdy('Sep 13, 2010')

#mdy('S 13, 2010')
# No formats found. Using S is not sufficient and R studio cannot interpret it

dmy('07-Dec-1941')

mdy('1-5-1998') # This one could be wrong, because it could be referring to either January 5th or May 1st 1998

dmy('21-5-1998') # This one is correct, as there is no 21 month, so it can only be reffering to May 21 1998

ymd_hm('2020-May-5 10:30 am')

ymd_hm('2020-May-5 10:30 am', tz = 'US/Pacific')

ymd_hm('2020-May-5 10:30 am', tz = 'America/Puerto_Rico')


```

## Chapter 12 Question 2a

```{r}
Birthday <- mdy('03-21-2003')

Today <- today()

SixtyFive <- Birthday + years(65)

TimeTilSixtyFive <- interval(Today, SixtyFive)

as.period(TimeTilSixtyFive)


```
## Question 2 b
```{r}
Age <- interval(Birthday, Today)

Age <- as.period(Age)


year(Age)

```
## Question 2 c

```{r}
nextBday <- Birthday + years(21)

nextBday 

```
## Question 2 d

```{r}

WaitTime <- interval(Today, nextBday)

WaitTime <- as.period(WaitTime, unit = 'days')

WaitTime


```

## Chapter 12 Question 2e
```{r}
WaitTime <- interval(Today, nextBday)

WaitTime <- as.period(WaitTime)

WaitTime

```
## Chapter 12 Question 3


```{r}

Call <- ymd_hm('2015-May-8 3:00 pm', tz = 'US/Arizona')

with_tz(Call, 'Pacific/Auckland')

```
## Chapter 12 Question 5 a

```{r}
library(mosaicData)


data("Births78")

Births78 <- Births78 %>% select(date,births)

head(Births78)




```

## Chapter 12 question 5b


```{r}
ggplot(Births78, aes(x= date, y = births)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs( title = "Number of Births vs. Date",
        x = "Date",
        y = "Number of Births")


```
There appears to be a weak positive linear relationship between number of births and time. Over time, the number of births seems to increase, but the model does not appear that it would have a very high R squared value. 

## Chapter 12 Question 5c

```{r}
Births78 <- Births78 %>% 
  mutate(dow = wday(date, label = TRUE, abbr = FALSE, ))

head(Births78)

```
## Chapter 12 Question 5d

```{r}
ggplot(Births78, aes(x = date, y = births, color = dow)) +
  geom_point() +
  geom_smooth( method = 'lm' ) +
  labs(title = "Number of Births vs. Date",
       x = "Date",
       y = "Number of Births")




```


